Manuscript draft

### 2019-05-31 manuscript/manuscript draft.Rmd
updated manuscript draft

Globally, forests play an important role in the carbon cycle.

Forests are estimated to sequester [x] carbon annually, making them a significant carbon sink, and an important component of global carbon dioxide budgets.

The productivity of forests shows variation with latitude, however the exact nature of this pattern and the mechanisms that drive it are poorly understood. On a global scale variation in primary productivity is likely to be climate-driven, meaning that achieving a better understanding of the climatic controls on forest productivity is essential for understanding and predicting the reponses and feedbacks of forests to climate change.

Understanding global patterns of net primary productivity in forest ecosystems is essential for understanding the global carbon cycle.

The relationship between primary productivity and latitude is unclear.

@@

>>>>

Globally, forests play an important role in the carbon cycle. Old growth forests alone are estimated to sequester up to 1.4 GtCyr superscript^-1^ [@Malhi1999], making them a significant carbon sink, and am important component of global carbon dioxide budgets [@Luyssaert2008]. Understanding the patterns and mechanisms of forest carbon cycling on a global scale is therefore of high importance in understanding the potential role of forests in mitigating climate change.

It is understood that the productivity of forests shows variation with latitude, with a general trend of increasing productivity towards the tropics, however the exact nature of this pattern and the mechanisms that drive it are poorly understood. Climate can be an important driver of productivity, particularly on a global scale; achieving a better understanding of the climatic controls on forest productivity will help to illuminate potential responses and feedbacks of forests to climate change.

@@

Data that control for stand age and standardize methodologies are required to resolve this question. Here, we use a comprehensive global database to explore global patterns in productivity.
